\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel Space

### 2012-05-18 evaluation.tex
fix some figs in eval

\newcommand\asdf[1]{\hspace{-0.05in}\footnotesize\bf{#1}\hspace{-0.05in}}
\revision{
\begin{table}[t]
	\begin{center}
	\small
	\begin{tabular}{|l||c|c|c|c|c|c||c|c|}
		\hline
		\multirow{2}{*}{\bf Group} & \multicolumn{6}{|c||}{\bf Minutes spent doing\dots} & \multicolumn{2}{|c|}{\bf Total time spent} \\
		\cline{2-9}
		& \asdf{annotating} & \asdf{config} & \asdf{student.c} & \asdf{fixing} & \asdf{customising} & \asdf{found races} & \asdf{required} & \asdf{refinement} \\
		\hline \hline
		% ntaha/jmchow
		\multirow{2}{*}{Group 1} & 35 & {\footnotesize \em N/A} & {\footnotesize \em N/A} & 5 & {\footnotesize \em N/A} & {\footnotesize \em N/A} & {\footnotesize \em N/A} & {\footnotesize \em N/A} \\
		\cline{2-9}
		& 5 & 30 & 10 & 100 & {\footnotesize \em N/A} & {\footnotesize \em N/A} & 145 & {\footnotesize \em N/A} \\
		\hline
		% echo/margaret
		\multirow{2}{*}{Group 2} & 20 & 30 & 10 & 80 & {\footnotesize \em N/A} & 10 & 140 & 10 \\
		\cline{2-9}
		& 15 & 45 & 30 & 60 & {\footnotesize \em N/A} & 30 & 150 & 30 \\
		\hline
		% tpassaro
		\multirow{2}{*}{Group 3} & 15 & 10 & 5 & 60 & 30 & 30 & 90 & 60 \\
		\cline{2-9}
		& 15 & 10 & 5 & 60 & 30 & 30 & 90 & 60 \\
		\hline
		% pjumde
		\multirow{2}{*}{Group 4} & 10 & 42 & 3 & 5 & 30 & {\footnotesize \em N/A} & 60 & 30 \\
		\cline{2-9}
		& 15 & 35 & {\footnotesize \em N/A} & 5 & 35 & {\footnotesize \em N/A} & {\footnotesize \em N/A} & 35 \\
		\hline
		% apodolsk
		Group 5 & 50 & 15 & {\footnotesize \em N/A} & 15 & {\footnotesize \em N/A} & {\footnotesize \em N/A} & {\footnotesize \em N/A} & {\footnotesize \em N/A} \\
		\hline
		Former TA & 40 & 20 & 3 & 95 & {\footnotesize \em N/A} & 30 & 158 & 30 \\
		\hline
		\hline
		{\bf Average } & {\bf 22 } & {\bf 26.33 } & {\bf 9.43 } & {\bf 48.5 } & {\bf 31.25 } & {\bf 26 } & {\bf 119 } & {\bf 36.43} \\
		\hline
	\end{tabular}
	\end{center}
	\caption{Self-reported times spent by users on each phase while using Landslide. ``N/A'' indicates a student reported spending no time on a particular phase. ``Required'' indicates the sum of the times from the first four phases; ``refinement'' inducates the sum from the last two phases.
	``N/A'' indicates that a user did not report spending any time on a phase; the ``required'' field is ``N/A'' if any of its represented phases are, and ``N/A'' fields are not reflected in the averages.}
	\label{fig:student-times}
\end{table}
\begin{figure}[h]
	\center
	\includegraphics[width=0.5\textwidth]{graphs/studence-pie.pdf}
	\caption{Average time breakdown for each phase of instrumenting a kernel with Landslide, based on student self-reported times.}
	\label{fig:student-pie}
\end{figure}

@@

@@

\begin{table}[t!]
	\begin{center}
	\footnotesize
	\begin{tabular}{|l||c|c|c|c|}
		\hline
		\multirow{2}{*}{\bf Kernel and test case} & \multicolumn{4}{c|}{\bf Decision points used} \\ % & \multirow{2}{*}{\bf Stress test} \\
		\cline{2-5}
		& {\bf default} & {\bf lock} & {\bf unlock} & {\bf both} \\
		\hline\hline
		POBBLES vanish/vanish (a) & \nobugnum{31.8}{0.6} & \bugnum{57.1}{1.7} & $\infty$ & $\infty$ \\
		\hline
		POBBLES vanish/vanish (b) & \nobugnum{32.0}{0.4} & \bugnum{51.5}{2.1} & \nobugnum{8057.9}{336.9} & $\infty$ \\
		\hline
		POBBLES wait/wait & \bugnum{23.3}{0.7} & \bugnum{27.9}{0.8} & \bugnum{27.9}{2.1} & \bugnum{41.6}{1.4} \\
		\hline
		POBBLES thread\_fork/vanish & \bugnum{22.0}{0.6} & \bugnum{37.4}{1.1} & \bugnum{27.6}{0.5} & \bugnum{72.0}{2.6} \\
		\hline
		LudicrOS vanish/vanish & \nobugnum{13.2}{0.2} & \bugnum{13.7}{0.7} & \bugnum{34.6}{1.1} & \bugnum{17.1}{0.3} \\
		\hline
		LudicrOS yield/vanish & \nobugnum{12.3}{0.3} & \bugnum{11.4}{0.4} & \nobugnum{27.4}{0.8} & \bugnum{11.7}{0.4} \\
		\hline
		\multicolumn{5}{c}{Key: \bugnum{seconds}{stddev} indicates bug found; \nobugnum{seconds}{stddev} indicates whole tree explored with no bug.} \\
	\end{tabular}
	\end{center}
	\caption{Comparison of time taken (in seconds) to find bugs using Landslide with various decision sets:
	the default set, consisting only of voluntary reschedules (Section~\ref{sec:components-arbiter}); and using custom decision points in addition to the default set: calls to \texttt{mutex\_lock}, calls to \texttt{mutex\_unlock}, and both.
	All numbers represent the average from 5 trials, with the standard deviations given in parentheses. ``$\infty$'' indicates that Landslide's search did not finish (after 8 hours).
	}
	\label{fig:numbers}
\end{table}
\revision{
\begin{figure}[h]
	\center
	\includegraphics[width=0.7\textwidth]{graphs/decisions.pdf}
	\caption{Bar graph visualisation of the exploration time in trials that did find bugs. The decision trees that did not expose bugs, and the ones that timed out, are not shown.}
	\label{fig:number-graph}
\end{figure}
}

@@

\newcommand\bugtree[1]{\textcolor{BrickRed}{\bf #1}}
\newcommand\nobugtree[1]{\textcolor{Blue}{[{\em #1}]}}
\begin{table}[t!]
	\begin{center}
	\footnotesize
	\begin{tabular}{|l|l||c|c|c|c|}
		\hline
		\multirow{2}{*}{\bf Kernel and test case} & \multirow{2}{*}{\bf Property of tree} & \multicolumn{4}{|c|}{\bf Decision points used} \\
		\cline{3-6}
		& & \bf default & \bf lock & \bf unlock & \bf both \\
		\hline\hline
		\multirow{4}{*}{POBBLES vanish/vanish (a)} & Decision points & \nobugtree{56} & \bugtree{1296} & N/A & N/A \\
		& Total backtracks   & \nobugtree{16} & \bugtree{376} & N/A & N/A \\
		& Average branch depth & \nobugtree{5} & \bugtree{19} & N/A & N/A \\
		\hline
		\multirow{4}{*}{POBBLES vanish/vanish (b)} & Decision points & \nobugtree{56} & \bugtree{1295} & \nobugtree{382071} & N/A \\
		& Total backtracks   & \nobugtree{16} & \bugtree{376} & \nobugtree{112706} & N/A \\
		& Average branch depth & \nobugtree{5} & \bugtree{17} & \nobugtree{16} & N/A \\
		\hline
		\multirow{4}{*}{POBBLES wait/wait} & Decision points & \bugtree{23} & \bugtree{102} & \bugtree{74} & \bugtree{378} \\
		& Total backtracks   & \bugtree{4} & \bugtree{17} & \bugtree{12} & \bugtree{56} \\
		& Average branch depth & \bugtree{6} & \bugtree{10} & \bugtree{9} & \bugtree{14} \\
		\hline
		\multirow{4}{*}{POBBLES thread\_fork/vanish} & Decision points & \bugtree{24} & \bugtree{394} & \bugtree{273} & \bugtree{2269} \\
		& Total backtracks   & \bugtree{5} & \bugtree{70} & \bugtree{56} & \bugtree{410} \\
		& Average branch depth & \bugtree{5} & \bugtree{16} & \bugtree{14} & \bugtree{23} \\
		\hline
		\multirow{4}{*}{LudicrOS vanish/vanish} & Decision points & \nobugtree{10} & \bugtree{16} & \bugtree{141} & \bugtree{42} \\
		& Total backtracks   & \nobugtree{2} & \bugtree{3} & \bugtree{48} & \bugtree{10} \\
		& Average branch depth & \nobugtree{2} & \bugtree{7} & \bugtree{9} & \bugtree{14} \\
		\hline
		\multirow{4}{*}{LudicrOS yield/vanish} & Decision points & \nobugtree{8} & \bugtree{5} & \nobugtree{149} & \bugtree{7} \\
		& Total backtracks   & \nobugtree{1} & \bugtree{0} & \nobugtree{43} & \bugtree{0} \\
		& Average branch depth & \nobugtree{2} & \bugtree{0} & \nobugtree{9} & \bugtree{0} \\
		\hline
	\end{tabular}
	\end{center}
	\caption{Information about the decision trees explored when finding bugs. As in the previous table, each test case was run with the four different sets of decision points. ``\nobugtree{X}'' means the tree was completely explored because Landslide did not find a bug in that configuration. ``\bugtree{X}'' reflects the portion of the tree that was explored before a bug was found.}
	\label{fig:trees}
\end{table}

>>>>

\newcommand\asdf[1]{\hspace{-0.05in}\footnotesize\bf{#1}\hspace{-0.05in}}
\revision{
\begin{table}[t]
	\begin{center}
	\small
	\begin{tabular}{|l||c|c|c|c|c|c||c|c|}
		\hline
		\multirow{2}{*}{\bf Group} & \multicolumn{6}{|c||}{\bf Minutes spent doing\dots} & \multicolumn{2}{|c|}{\bf Total time spent} \\
		\cline{2-9}
		& \asdf{annotating} & \asdf{config} & \asdf{student.c} & \asdf{fixing} & \asdf{customising} & \asdf{found races} & \asdf{required} & \asdf{refinement} \\
		\hline \hline
		% ntaha/jmchow
		\multirow{2}{*}{Group 1} & 35 & {\footnotesize \em N/A} & {\footnotesize \em N/A} & 5 & {\footnotesize \em N/A} & {\footnotesize \em N/A} & {\footnotesize \em N/A} & {\footnotesize \em N/A} \\
		\cline{2-9}
		& 5 & 30 & 10 & 100 & {\footnotesize \em N/A} & {\footnotesize \em N/A} & 145 & {\footnotesize \em N/A} \\
		\hline
		% echo/margaret
		\multirow{2}{*}{Group 2} & 20 & 30 & 10 & 80 & {\footnotesize \em N/A} & 10 & 140 & 10 \\
		\cline{2-9}
		& 15 & 45 & 30 & 60 & {\footnotesize \em N/A} & 30 & 150 & 30 \\
		\hline
		% tpassaro
		\multirow{2}{*}{Group 3} & 15 & 10 & 5 & 60 & 30 & 30 & 90 & 60 \\
		\cline{2-9}
		& 15 & 10 & 5 & 60 & 30 & 30 & 90 & 60 \\
		\hline
		% pjumde
		\multirow{2}{*}{Group 4} & 10 & 42 & 3 & 5 & 30 & {\footnotesize \em N/A} & 60 & 30 \\
		\cline{2-9}
		& 15 & 35 & {\footnotesize \em N/A} & 5 & 35 & {\footnotesize \em N/A} & {\footnotesize \em N/A} & 35 \\
		\hline
		% apodolsk
		Group 5 & 50 & 15 & {\footnotesize \em N/A} & 15 & {\footnotesize \em N/A} & {\footnotesize \em N/A} & {\footnotesize \em N/A} & {\footnotesize \em N/A} \\
		\hline
		Former TA & 40 & 20 & 3 & 95 & {\footnotesize \em N/A} & 30 & 158 & 30 \\
		\hline
		\hline
		{\bf Average } & {\bf 22 } & {\bf 26.33 } & {\bf 9.43 } & {\bf 48.5 } & {\bf 31.25 } & {\bf 26 } & {\bf 119 } & {\bf 36.43} \\
		\hline
	\end{tabular}
	\end{center}
	\caption{Self-reported times spent by users on each phase while using Landslide. ``N/A'' indicates a student reported spending no time on a particular phase. ``Required'' indicates the sum of the times from the first four phases; ``refinement'' inducates the sum from the last two phases.
	``N/A'' indicates that a user did not report spending any time on a phase; the ``required'' field is ``N/A'' if any of its represented phases are, and ``N/A'' fields are not reflected in the averages.}
	\label{fig:student-times}
\end{table}

@@

\begin{wrapfigure}{r}{0.4\textwidth}
	\center
	\includegraphics[width=0.4\textwidth]{graphs/studence-pie.pdf}
	\caption{Average time breakdown for each phase of instrumenting a kernel with Landslide, based on student self-reported times.}
	\label{fig:student-pie}
\end{wrapfigure}

@@

\begin{table}[t!]
	\begin{center}
	\small
	\begin{tabular}{|l||c|c|c|c|}
		\hline
		\multirow{2}{*}{\bf Kernel and test case} & \multicolumn{4}{c|}{\bf Decision points used} \\ % & \multirow{2}{*}{\bf Stress test} \\
		\cline{2-5}
		& {\bf default} & {\bf lock} & {\bf unlock} & {\bf both} \\
		\hline\hline
		POBBLES vanish/vanish (a) & \nobugnum{31.8}{0.6} & \bugnum{57.1}{1.7} & $\infty$ & $\infty$ \\
		\hline
		POBBLES vanish/vanish (b) & \nobugnum{32.0}{0.4} & \bugnum{51.5}{2.1} & \nobugnum{8057.9}{336.9} & $\infty$ \\
		\hline
		POBBLES wait/wait & \bugnum{23.3}{0.7} & \bugnum{27.9}{0.8} & \bugnum{27.9}{2.1} & \bugnum{41.6}{1.4} \\
		\hline
		POBBLES thread\_fork/vanish & \bugnum{22.0}{0.6} & \bugnum{37.4}{1.1} & \bugnum{27.6}{0.5} & \bugnum{72.0}{2.6} \\
		\hline
		LudicrOS vanish/vanish & \nobugnum{13.2}{0.2} & \bugnum{13.7}{0.7} & \bugnum{34.6}{1.1} & \bugnum{17.1}{0.3} \\
		\hline
		LudicrOS yield/vanish & \nobugnum{12.3}{0.3} & \bugnum{11.4}{0.4} & \nobugnum{27.4}{0.8} & \bugnum{11.7}{0.4} \\
		\hline
	\end{tabular}
	\end{center}
	\caption{Comparison of time taken (in seconds) to find bugs using Landslide with various decision sets:
	the default set, consisting only of voluntary reschedules (Section~\ref{sec:components-arbiter}); and using custom decision points in addition to the default set: calls to \texttt{mutex\_lock}, calls to \texttt{mutex\_unlock}, and both.
	All numbers represent the average from 5 trials, with the standard deviations given in parentheses. \\
	Key: \bugnum{seconds}{\footnotesize stddev} indicates bug found; \nobugnum{seconds}{\footnotesize stddev} indicates whole tree explored with no bug.
	``$\infty$'' indicates that Landslide's search did not finish (after 8 hours).
	}
	\label{fig:numbers}
\end{table}
\revision{
\begin{figure}[h]
	\center
	\includegraphics[width=0.8\textwidth]{graphs/decisions.pdf}
	\caption{Bar graph visualisation of the exploration time in trials that did find bugs. The decision trees that did not expose bugs and the ones that timed out are not shown.}
	\label{fig:number-graph}
\end{figure}
}

@@

\newcommand\bugtree[1]{\textcolor{BrickRed}{\bf #1}}
\newcommand\nobugtree[1]{\textcolor{Blue}{[{\em #1}]}}
\begin{table}[t!]
	\begin{center}
	\small
	\begin{tabular}{|l|l||c|c|c|c|}
		\hline
		\multirow{2}{*}{\bf Kernel and test case} & \multirow{2}{*}{\bf Property of tree} & \multicolumn{4}{|c|}{\bf Decision points used} \\
		\cline{3-6}
		& & \bf default & \bf lock & \bf unlock & \bf both \\
		\hline\hline
		\multirow{4}{*}{POBBLES vanish/vanish (a)} & Decision points & \nobugtree{56} & \bugtree{1296} & N/A & N/A \\
		& Total backtracks   & \nobugtree{16} & \bugtree{376} & N/A & N/A \\
		& Average branch depth & \nobugtree{5} & \bugtree{19} & N/A & N/A \\
		\hline
		\multirow{4}{*}{POBBLES vanish/vanish (b)} & Decision points & \nobugtree{56} & \bugtree{1295} & \nobugtree{382071} & N/A \\
		& Total backtracks   & \nobugtree{16} & \bugtree{376} & \nobugtree{112706} & N/A \\
		& Average branch depth & \nobugtree{5} & \bugtree{17} & \nobugtree{16} & N/A \\
		\hline
		\multirow{4}{*}{POBBLES wait/wait} & Decision points & \bugtree{23} & \bugtree{102} & \bugtree{74} & \bugtree{378} \\
		& Total backtracks   & \bugtree{4} & \bugtree{17} & \bugtree{12} & \bugtree{56} \\
		& Average branch depth & \bugtree{6} & \bugtree{10} & \bugtree{9} & \bugtree{14} \\
		\hline
		\multirow{4}{*}{POBBLES thread\_fork/vanish} & Decision points & \bugtree{24} & \bugtree{394} & \bugtree{273} & \bugtree{2269} \\
		& Total backtracks   & \bugtree{5} & \bugtree{70} & \bugtree{56} & \bugtree{410} \\
		& Average branch depth & \bugtree{5} & \bugtree{16} & \bugtree{14} & \bugtree{23} \\
		\hline
		\multirow{4}{*}{LudicrOS vanish/vanish} & Decision points & \nobugtree{10} & \bugtree{16} & \bugtree{141} & \bugtree{42} \\
		& Total backtracks   & \nobugtree{2} & \bugtree{3} & \bugtree{48} & \bugtree{10} \\
		& Average branch depth & \nobugtree{2} & \bugtree{7} & \bugtree{9} & \bugtree{14} \\
		\hline
		\multirow{4}{*}{LudicrOS yield/vanish} & Decision points & \nobugtree{8} & \bugtree{5} & \nobugtree{149} & \bugtree{7} \\
		& Total backtracks   & \nobugtree{1} & \bugtree{0} & \nobugtree{43} & \bugtree{0} \\
		& Average branch depth & \nobugtree{2} & \bugtree{0} & \nobugtree{9} & \bugtree{0} \\
		\hline
	\end{tabular}
	\end{center}
	\caption{Information about the decision trees explored when finding bugs. As in the previous table, each test case was run with the four different sets of decision points. ``\nobugtree{X}'' means the tree was completely explored because Landslide did not find a bug in that configuration. ``\bugtree{X}'' reflects the portion of the tree that was explored before a bug was found.}
	\label{fig:trees}
\end{table}
